Cluster Difference Imaging Photometric Survey (CDIPS) II: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-17 paper/ms.tex
minor

\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A
Jupiter-Sized Planet Candidate in IC~2602}

@@

\begin{abstract}
We validate the planetary nature of the transiting planet TOI 837.01.
We characterize the system using data from the NASA {\it Transiting
  Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
  ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
  MPG2.2/FEROS, and AAT/Veloce.
We find that TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the
``Southern Pleiades''). 
The star is therefore 30$\pm$20 million years old.
The validated planet is warm ($P = 8.YY\,{\rm d}$) and likely
  Jupiter-sized. 
However, its transits are grazing: $b > 0.92$ at 3$\sigma$.
From transit photometry alone, the planetary size lies within
  0.58--3.87 $R_{\rm Jup}$, due to the degeneracy
  between the planetary size and its impact parameter.
From radial velocity monitoring, we find that its mass is less than
  2.XX $M_{\rm Jup}$ (3$\sigma$).
This mass limit requires the planetary size to be below
  $\approx$2.0$R_{\rm Jup}$.
Non-planetary explanations for the data, most notably hierarchical or
  background eclipsing binaries, are argued to be highly unlikely on
  statistical grounds.
TOI 837.01 therefore tentatively joins the ranks of adolescent
  exoplanets orbiting bright host stars. Further analysis of its mass,
  atmosphere, and obliquity could confirm its planetary nature beyond
  doubt, and are worthwhile because young planets do interesting
  things.
\end{abstract}

@@

\begin{figure}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f6.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Spectral energy distribution of \tn\ from archival
    photometry.}
    {\bf Keivan: please describe, and if possible, send me the data
    (photometry + the atmosphere model) used to generate the plot so I
    can regenerate it in a consistent style with the rest of the paper}
    \label{fig:sed}
	}
\end{figure}

@@

>>>>

\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A Validated
Jupiter-Sized Planet in IC~2602}

@@

\begin{abstract}
We present the discovery of TOI 837.01 and its validation as
a transiting planet.
We characterize the system using data from the NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA Gaia mission, ground-based photometry, and spectroscopy from CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.
We find that TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the
``Southern Pleiades''). 
The star is therefore 30$\pm$20 million years old.
The validated planet is warm ($P = 8.YY\,{\rm d}$) and roughly
  Jupiter-sized. 
However, its transits are grazing: $b > 0.92$ at 3$\sigma$.
From TESS photometry alone, the planetary size lies within
  0.58--3.87 $R_{\rm Jup}$, due to the degeneracy
  between the planetary size and the impact parameter of the transit.
From radial velocity monitoring, we limit the mass of planet
to less than 2.XX $M_{\rm Jup}$ (3$\sigma$).
Grazing transits are cause for concern, as they most often are indicative of astrophysical false positive scenarios.
Our combined data render such scenarios highly unlikely.
Multi-color photometry requires eclipsing companions to be nearly the same
colors as TOI$\,$837, eliminating hierarchical eclipsing
binary scenarios.
Background eclipsing binary scenarios are limited by speckle
imaging, but formally remain a 0.2\% possibility.
TOI 837.01 therefore joins the ranks of adolescent
  exoplanets orbiting bright host stars. Further analysis of its mass,
  atmosphere, and obliquity should confirm its planetary nature beyond
  doubt, and are worthwhile because young planets do interesting
  things.
\end{abstract}

@@

% TODO: decide whether to include

% \begin{figure}[t!]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.48\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{
%     {\bf Spectral energy distribution of \tn\ from archival
%     photometry.}
%     {\bf Keivan: please describe, and if possible, send me the data
%     (photometry + the atmosphere model) used to generate the plot so I
%     can regenerate it in a consistent style with the rest of the paper}
%     \label{fig:sed}
% 	}
% \end{figure}

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Multicolor photometry from the El Sauce 0.36m.}
		\label{fig:multicolor}
	}
\end{figure*}
